Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-16 paper/paper.tex
minor typos

so that the right-hand side is nonegative \citep[eq.(84)]{lapidoth_capacity_2003}.

@@

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it in automatic music
transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
and hold-out the same validation and test splits. During each training epoch we sample $1000$
mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
full window of $4096$ samples picked from each waveform and transformed from $\real$ to
$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.

@@

    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of non-negative integrals}]

>>>>

so that the right-hand side is nonnegative \citep[eq.(84)]{lapidoth_capacity_2003}.

@@

% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
musical compositions. Following \citet{trabelsi_deep_2017}, we use it in automatic music
transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
and hold-out the same validation and test splits. During each training epoch we sample $1000$
mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
full window of $4096$ samples picked from each waveform and transformed from $\real$ to
$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.

@@

    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of nonnegative integrals}]
